Spatiotemporal models of DO

### 2020-07-09 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
merge ROMs data with trawl data and check against CTD and sdmTMB model

```{r setup}
library(tidyverse)
library(sdmTMB)
library(future)
library(dplyr)
```

@@

>>>>

```{r setup}
library(tidyverse)
library(sdmTMB)
# library(future)
library(dplyr)
```

@@

```{r eval=F}
# test against ROMS
events_roms <- readRDS("data/roms_temp_by_events2.rds") %>% select(fishing_event_id, roms, year)

predictions <- left_join(predictions, events_roms)

cor(predictions$roms, predictions$est, use = "pairwise.complete.obs")
cor(predictions$roms, predictions$temperature_c, use = "pairwise.complete.obs")

ggplot(predictions, aes(roms, est, colour = -depth)) + geom_point(alpha=0.3) + 
  facet_wrap(~year) + coord_cartesian(xlim = c(2,13), ylim = c(2,13)) +
  geom_abline(intercept = 0, slope = 1) +
  gfplot::theme_pbs()

ggplot(predictions, aes(roms, temperature_c, colour = DOY)) + geom_point(alpha=0.3) +
  facet_wrap(~year) + coord_cartesian(xlim = c(2,13), ylim = c(2,13)) +
  geom_abline(intercept = 0, slope = 1) +
  scale_colour_viridis_c() +
  gfplot::theme_pbs()

ggplot(predictions, aes(DOY, (roms-temperature_c), colour = -depth)) + geom_point(alpha=0.3) +
  facet_wrap(~year) + #coord_cartesian(xlim = c(2,13), ylim = c(2,13)) +
  geom_abline(intercept = 0, slope = 0) +
  scale_colour_viridis_c() +
  gfplot::theme_pbs()

ggplot(predictions, aes(DOY, (est-roms), colour = -depth)) + geom_point(alpha=0.3) +
  facet_wrap(~year) + #coord_cartesian(xlim = c(2,13), ylim = c(2,13)) +
  geom_abline(intercept = 0, slope = 0) +
  scale_colour_viridis_c() +
  gfplot::theme_pbs()

p_nd <- readRDS((here::here("analysis/VOCC/data/predicted-DO-2020-06-20-more2016-roms.rds")))

cor(p_nd$roms_temp, p_nd$temp, use = "pairwise.complete.obs")

ggplot(p_nd, aes(roms_temp, temp, colour = -depth)) + geom_point(alpha=0.04) + 
  facet_wrap(~year) + coord_cartesian(xlim = c(2,13), ylim = c(2,13)) +
  geom_abline(intercept = 0, slope = 1) +
  gfplot::theme_pbs()
